Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-05 paper/main.tex
Updates

To tackle these limitations, we draw inspiration from modification indices in
specification search. Modification indices provide ranking for potential model
modification based on their impact on the model's fit, allowing us to
prioritize most meaningful modifications. Similarly, we propose a method for
ranking CI test violations to help us focus on the most critical
inconsistencies in the model. To determine this ranking we utilize a measure of
conditional association between variables in combination with p-values from the
CI test. This approach helps us in tackling all the three issues outlined
above. The measure of association allows us to test for existing edges, as well
as not only rely on p-value to make decision whether a CI test holds. The
ranking helps us in focusing on the most critical violations.

>>>>

To tackle these limitations, we draw inspiration from modification indices in
specification search. Modification indices provide ranking for potential model
modification based on their impact on the model's fit, allowing us to
prioritize most meaningful modifications.  Similarly, we propose a method for
ranking CI test violations to help us focus on the most critical
inconsistencies in the model. To determine this ranking we utilize a measure of
conditional association between variables in combination with p-values from the
CI test. This approach addresses all three of the issues outlined above. The
measure of association allows us to evaluate the validity of existing edges. It
reduces our reliance on p-values alone for deciding whether the CI test holds.
The ranking helps us prioritize the most critical violations, making it feasible 
to focus on the areas that most improve the model's fit.
